\thetitle

### 2021-04-30 writing/introduction.tex
Say what practice means at the end of intro

The paper's {\it second contribution\/} is a set of {\em results from
applying the evaluation method to three distinct blame assignment
strategies in approximately 72,000 different scenarios\/} (see
sec.~\ref{sec:results}): (1)~{\it Transient\/}, i.e. Reticulated's
tracking of typed/untyped boundaries~\citep{vss-popl-2017}; (2)~{\it
Natural\/}, i.e. Typed Racket's use of a higher-order contract system and
its blame assignment~\citep{ff-icfp-2002}; and (3) {\it Erasure\/}, i.e.
the approach of industrial systems, which forgo blame in favor of error
messages from the safety checks of the underlying language. The results
(see sec.~\ref{sec:discussion}) are at least somewhat surprising.  In
principle they validate the conjectures behind the work of theoreticians.
First, a good blame assignment strategy helps with the search for
impedance mismatches between the specified types and the behavior of
untyped components.  Second, Natural's wrapper-based blame tracking is
more useful than Transient's ``collective blame'' tracking algorithm,
which in turn is superior to Erasure. {\em But\/}, the application of the
method also indicates problems with the expectations of theoreticians. The
first problem concerns the difference between the methods; neither is {\it
Natural\/} vastly more useful than {\it Transient\/} nor are the two
blame assignment methods highly superior to {\it Erasure\/}.  The second
one is that the cost of Transient's blame can be huge.  In turn, these
problems suggest that, on one hand, the existing theory does not predict
practice properly, and on the other hand, the existing practice may need
additional experiments to collect more data.

>>>>

The paper's {\it second contribution\/} is a set of {\em results from
applying the evaluation method to three distinct blame assignment
strategies in approximately 72,000 different scenarios\/} (see
sec.~\ref{sec:results}): (1)~{\it Transient\/}, i.e. Reticulated's
tracking of typed/untyped boundaries~\citep{vss-popl-2017}; (2)~{\it
Natural\/}, i.e. Typed Racket's use of a higher-order contract system and
its blame assignment~\citep{ff-icfp-2002}; and (3) {\it Erasure\/}, i.e.
the approach of industrial systems, which forgo blame in favor of error
messages from the safety checks of the underlying language. The results
(see sec.~\ref{sec:discussion}) are at least somewhat surprising.  In
principle they validate the conjectures behind the work of theoreticians.
First, a good blame assignment strategy helps with the search for
impedance mismatches between the specified types and the behavior of
untyped components.  Second, Natural's wrapper-based blame tracking is
more useful than Transient's ``collective blame'' tracking algorithm,
which in turn is superior to Erasure. {\em But\/}, the application of the
method also indicates problems with the expectations of theoreticians. The
first problem concerns the difference between the methods; neither is {\it
Natural\/} vastly more useful than {\it Transient\/} nor are the two
blame assignment methods highly superior to {\it Erasure\/}.  The second
one is that the cost of Transient's blame can be huge.  In turn, these
problems suggest that, on one hand, the existing theory does not properly
predict practice (i.e. the behavior of blame in real systems with real programs),
and on the other hand, the existing practice may need
additional experiments to collect more data.
